---
title: "Figures for Matrix Variate Classification"
author: "Geoffrey Thompson et al"
date: "May 2021"
output: 
  pdf_document:
    keep_tex: true
    fig_crop: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE)
```

## Read Knife Data

```{r cars}
library('scales')
library('ggplot2')
library('lme4')
library('psych')
library('reshape2')
library('MASS')
devtools::load_all('./MixMatrix_0.1.0/')
library('CholWishart')
library('dplyr')
library('tidyr')



cor.set1 = read.csv(file =   "data/Correlationsset1.csv", check.names = FALSE, header = TRUE)[,-1]
cor.set2 = read.csv(file =   "data/Correlationsset2.csv", check.names = FALSE, header = TRUE)[,-1]
cor.set3 = read.csv(file =   "data/Correlationsset3.csv", check.names = FALSE, header = TRUE)[,-1]
cor.set4 = read.csv(file =   "data/Correlations S-10-9-02-truncated.csv", check.names = FALSE, header = TRUE)[,-1]
cor.set5 = read.csv(file =   "data/Correlations K-9-9-truncated.csv", check.names = FALSE, header = TRUE)[,-1]
cor.set6 = read.csv(file =   "data/Correlations S-10-9-10-truncated.csv", check.names = FALSE, header = TRUE)[,-1]
                  
### sets 2 and 3 are the replicates, so left out of this analysis.
totalcorset = rbind(cor.set1,cor.set5, cor.set4, cor.set6)

totalcorset$zfive = fisherz(totalcorset$`5-10`)
totalcorset$zten = fisherz(totalcorset$`10-20`)
totalcorset$repetition = factor(totalcorset$set)
totalcorset$img = factor(totalcorset$img)
matchset = totalcorset[totalcorset$match == "match",]
matchset = droplevels(matchset)
```

There are two types of data contained in this supplement. The first are the inputs: the correlations in various frequency bands between the imaged knife bases and tips. The second are model outputs: after a model is trained on one set of knives, the outputted log-odds of being a match are computed for each base-tip pair comparison in all of the sets. Other R scripts do those calculations, this workbook creates figures and does some computations.

```{r histplot, fig.width = 6, fig.height = 2.5}
### this is a manually resphaped version of replicate 2. 
### there isn't a particular reason why the second replicate was chosen
### The other ones look similar.
longfreq <- read.csv("data/corr-k-9-9-rep-2-long.csv")

longfreq$band = factor(longfreq$band, levels = c("5-10", "10-20", "20-30", "30-40", "40-50"))

histplot <- ggplot(longfreq, aes(x = correlation, fill = match)) + 
  geom_histogram(alpha = 0.8, position = "identity", bins = 30) +
  facet_wrap(~band, nrow = 1)+
  theme_bw()+
  xlab("Cross-correlations")+
  ylab("Count")+
  labs(fill = "Match")+
  scale_fill_manual(values=c("#D94801", "#238B45"), labels = c("match", "non-match"))+
  theme(legend.position = "bottom", legend.title = element_blank())+
  NULL
histplot

```


## Read LogOdds Data

This data is for the "consecutive" image analysis - taking all subsets with a specified overlap. 

This trains on all nine images (with 75% overlap, labeled from 1 to 9) and tests on, eg for subsets of size 3, 123, 234, 345, 456, 567, 678, and 789. This also trains on 5 images (1, 3, 5, 7, 9) for 50% overlap and 3 images (1, 5, and 9) for 0% and does a similar analysis. 


```{r odds, echo=FALSE}
finalfiles = list.files(pattern="final", path = "./oddsconsec/", full.names = TRUE)
#finalfiles

files159 = list.files(pattern="-0-df", path = "./oddsconsec/", full.names = TRUE)

odds159 = do.call("rbind",lapply(files159,FUN=function(files){read.table(files,header=TRUE, sep=",")})) %>% mutate(sets = "159")


files13579 = list.files(pattern="50-df", path = "./oddsconsec/", full.names = TRUE)

odds13579 = do.call("rbind",lapply(files13579,FUN=function(files){read.table(files,header=TRUE, sep=",")})) %>% mutate(sets = "13579")

filesall = list.files(pattern="all-df", path = "./oddsconsec/", full.names = TRUE)

oddsall = do.call("rbind",lapply(filesall,FUN=function(files){read.table(files,header=TRUE, sep=",")})) %>% mutate(sets = "all")

finalodds = rbind(odds159, odds13579,oddsall)
# removing because these are big.
rm(odds13579)
rm(odds159)
rm(oddsall)

```

This is a summary of log odds of being a match for models trained on 9 images and tested on 3 images for various degrees of freedom (mostly a diagnostic plot, it is not in the paper).

```{r demoplot, eval = TRUE}
newfacetlabels = c("K-1-1" = "K-9-06 rep 1", "K-1-2" = "K-9-06 rep 2", "K-1-3" = "K-9-06 rep 3", "K-2" = "K-9-9-01", "S-1" = "S-10-9-10-01", "S-10-09-02-01" = "S-2")



postlogplot <- ggplot(data = filter(finalodds, k == 3), aes(x = match, y = classes/log(10))) +
  labs(title = "Posterior log odds ratio for each surface", x = "", 
       y = expression(paste(Log[10]," odds of match"))) +
  geom_boxplot() + 
  geom_hline(yintercept = 0) +
  facet_grid(df~sets, labeller = labeller(model = newfacetlabels), scales = "free_y") +
  theme_bw() +
  NULL

postlogplot



```

## Tables of results

```{r tables, results = "as-is", fig.height=3, fig.width=3.5}
finalodds <- finalodds %>% mutate(
  TN = case_when(
    (matching == "nonmatch") & (classes < 0) ~ 1,
    TRUE ~ 0),
  FP = case_when(
    (matching == "nonmatch") & (classes > 0) ~ 1,
    TRUE ~ 0),
  FN = case_when(
    (matching == "match") & (classes < 0) ~ 1,
    TRUE ~ 0)
) %>% mutate(
  TP = case_when(
    (match == "match") & (classes > 0) ~ 1,
    TRUE ~ 0))

finalodds$factordf = ordered(finalodds$df, levels = c("3", "5", "10", "15", "20", "30"))


finalodds %>% group_by(factordf, k) %>% filter(sets == "all") %>% 
  dplyr::summarize(CountFP = sum(FP), CountFN = sum(FN), CountTP = sum(TP), CountTN = sum(TN)) %>%
  mutate(CountP = CountFN + CountTP, CountN = CountFP + CountTN) -> allsummary

finalodds %>% group_by(factordf, k) %>% filter(sets == "13579") %>% 
  dplyr::summarize(CountFP = sum(FP), CountFN = sum(FN), CountTP = sum(TP), CountTN = sum(TN)) %>%
  mutate(CountP = CountFN + CountTP, CountN = CountFP + CountTN) -> fiftysummary

finalodds %>% group_by(factordf, k) %>% filter(sets == "159") %>%
  dplyr::summarize(CountFP = sum(FP), CountFN = sum(FN), CountTP = sum(TP), CountTN = sum(TN)) %>%
  mutate(CountP = CountFN + CountTP, CountN = CountFP + CountTN) -> zerosummary

knitr::kable(allsummary)

knitr::kable(fiftysummary)

knitr::kable(zerosummary)

ggplot(data = allsummary, aes(x = factor(k), y = 100*CountFP/CountN, fill = factordf, color = factordf)) + 
  geom_bar(stat = 'identity', width=.5, position = "dodge") + 
  xlab("Number of images") + 
  ylab("False positive rate (%)")+
      labs(fill = "Degrees of \nfreedom", color = "Degrees of \nfreedom")+
    theme_bw() +
    theme(legend.position = "bottom")+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  NULL

ggplot(data = allsummary, aes(x = factor(k), y = 100*CountFN/CountP, fill = factordf, color = factordf)) + 
  geom_bar(stat = 'identity', width=.5, position = "dodge") + 
  xlab("Number of images") + 
  ylab("False negative rate (%)")+
      labs(fill = "Degrees of \nfreedom", color = "Degrees of \nfreedom")+
    theme_bw() +
      theme(legend.position = "bottom")+
    scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  NULL

ggplot(data = fiftysummary, aes(x = factor(k), y = 100*CountFP/CountN, fill = factordf, color = factordf)) + 
  geom_bar(stat = 'identity', width=.5, position = "dodge") + 
  xlab("Number of images") + 
  ylab("False positive rate (%)")+
      labs(fill = "Degrees of \nfreedom", color = "Degrees of \nfreedom")+
    theme_bw() +
      theme(legend.position = "bottom")+
    scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  ggtitle("50% overlap")+
  NULL

ggplot(data = fiftysummary, aes(x = factor(k), y = 100*CountFN/CountP, fill = factordf, color = factordf)) + 
  geom_bar(stat = 'identity', width=.5, position = "dodge") + 
  xlab("Number of images") + 
  ylab("False negative rate (%)")+
      labs(fill = "Degrees of \nfreedom", color = "Degrees of \nfreedom")+
    theme_bw() +
        theme(legend.position = "bottom")+
    scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  NULL

ggplot(data = zerosummary, aes(x = factor(k), y = 100*CountFP/CountN, fill = factordf, color = factordf)) + 
  geom_bar(stat = 'identity', width=.5, position = "dodge") + 
  xlab("Number of images") + 
  ylab("False positive rate (%)")+
      labs(fill = "Degrees of \nfreedom", color = "Degrees of \nfreedom")+
    theme_bw() +
        theme(legend.position = "bottom")+
    scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  NULL

ggplot(data = zerosummary, aes(x = factor(k), y = 100*CountFN/CountP, fill = factordf, color = factordf)) + 
  geom_bar(stat = 'identity', width=.5, position = "dodge") + 
  xlab("Number of images") + 
  ylab("False negative rate (%)")+
      labs(fill = "Degrees of \nfreedom", color = "Degrees of \nfreedom")+
    theme_bw() +
       theme(legend.position = "bottom")+
    scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  NULL


```

```{r moresets, fig.height=4, fig.width=5.5}

ggplot(data = allsummary, aes(x = factor(k), fill = factordf, color = factordf)) + 
  geom_hline(yintercept = 0, color = "gray")+
  geom_bar(aes(y = -100*CountFP/CountN), stat = 'identity', width=.5, position = "dodge") +
  annotate( "text", x=6, y=-0.25, label="False Negative Rate", hjust=0) +
  geom_bar(aes(y = 100*CountFN/CountP), stat = 'identity', width=.5, position = "dodge") + 
  annotate("text", x=6, y=0.35, label="False Positive Rate", hjust=0) +
  xlab("Number of images") + 
  ylab("Rate (%)")+
  labs(fill = "DF", color = "DF", )+
  theme_bw() +
  theme(legend.position = c(0.8, 0.55), legend.direction="horizontal",
        legend.background = element_rect(fill = "white", color = "black"))+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  NULL
ggsave("fp-fn-combined.pdf", height= 4, width = 5.5)

```


```{r moresetstwo, fig.height=2.5, fig.width=5.5}


fiftysummary_tmp <- fiftysummary %>% mutate(set = "50% overlap")
zerosummary_tmp <- zerosummary %>% mutate(set = "0% overlap")

fiftyzero = rbind(fiftysummary_tmp, zerosummary_tmp)


ggplot(data = fiftyzero, aes(x = factor(k), y = 100*CountFP/CountN, fill = factordf, color = factordf)) + 
  geom_bar(stat = 'identity', width=.5, position = "dodge") + 
  xlab("Number of images") + 
  ylab("False positive rate (%)")+
  facet_grid(rows = ~set, scales = "free_x", space = "free_x")+
  labs(fill = "DF", color = "DF")+
  theme_bw() +
  theme(legend.position = c(0.8, 0.75), legend.direction="horizontal",
        legend.background = element_rect(fill = "white", color = "black"))+
  scale_fill_brewer(palette = "Dark2")+
  scale_color_brewer(palette = "Dark2")+
  NULL
ggsave("fifty-zero-overlap.pdf", height = 4, width = 5.5)

```


```{r subsetsoverlap}

nooverlap <- ggplot(data = (filter(finalodds, k == 3, sets == "159") ), aes(x = match, y = classes/log(10))) +
  labs(title = "Posterior log odds ratio for 50% overlap", x = "", 
       y = expression(paste(Log[10]," odds of match"))) +
  geom_boxplot() + 
  geom_hline(yintercept = 0) +
  facet_wrap(~factordf,  scales = "free_y") +
      theme(title = element_text(size = 9), legend.position="bottom", legend.text = element_text(size=7),
          legend.title = element_text(size = 8), axis.text =  element_text(size=7), axis.title = element_text(size=8),
          axis.text.y = element_text( angle = 90, hjust = .5),
          strip.text = element_text(size = 7), plot.margin=grid::unit(c(0,0,0,0), "mm"),
          strip.background = element_rect(fill = "slategray2"))+
   theme_bw() +
  NULL



fiftyoverlap <- ggplot(data = (filter(finalodds, k == 5, sets == "13579") ), aes(x = match, y = classes/log(10))) +
  labs(title = "Posterior log odds ratio for 50% overlap", x = "", 
       y = expression(paste(Log[10]," odds of match"))) +
  geom_boxplot() + 
  geom_hline(yintercept = 0) +
  facet_wrap(~factordf,  scales = "free_y") +
      theme(title = element_text(size = 9), legend.position="bottom", legend.text = element_text(size=7),
          legend.title = element_text(size = 8), axis.text =  element_text(size=7), axis.title = element_text(size=8),
          axis.text.y = element_text( angle = 90, hjust = .5),
          strip.text = element_text(size = 7), plot.margin=grid::unit(c(0,0,0,0), "mm"),
          strip.background = element_rect(fill = "slategray2"))+
  theme_bw() +
  NULL

fiftyoverlap



seventyfive <- ggplot(data = (filter(finalodds, k == 3, sets == "all") ), aes(x = match, y = classes/log(10))) +
  labs(title = "Posterior log odds ratio for 75% overlap", x = "", 
       y = expression(paste(Log[10]," odds of match"))) +
  geom_boxplot() + 
  geom_hline(yintercept = 0) +
  facet_wrap(~factordf,  scales = "free_y") +
      theme(title = element_text(size = 9), legend.position="bottom", legend.text = element_text(size=7),
          legend.title = element_text(size = 8), axis.text =  element_text(size=7), axis.title = element_text(size=8),
          axis.text.y = element_text( angle = 90, hjust = .5),
          strip.text = element_text(size = 7), plot.margin=grid::unit(c(0,0,0,0), "mm"),
          strip.background = element_rect(fill = "slategray2"))+
  theme_bw() +
  NULL

seventyfive




```


Plots for df = 10.

```{r finalplot, dev = "pdf", fig.width = 5, eval = TRUE}

ggplot(data = (filter(finalodds, !(model %in% c("2","3")), sets == "all", df == 10)),mapping = aes(x = factor(k), y = logodds, fill = matching)) +
    geom_boxplot(position = position_dodge(width = .3)) +
    theme_bw(base_size = 13) +
  xlab("Number of images")+
    theme(legend.position = c(0.01,.99), legend.justification = c(0,1), legend.background = element_rect(), panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    geom_hline(yintercept = 0) + 
    annotate("text", x=.6,y=0.65,label = "p = 0.5", hjust=0)+
    geom_hline(yintercept = logit(.99)/log(10), linetype = 2, color = "grey") +
        annotate("text", x=.6,y=(.65+logit(.99)/log(10)),label = "p = 0.99", hjust=0)+
    geom_hline(yintercept = logit(.01)/log(10), linetype = 2, color = "grey") +
     annotate("text", x=.6,y=0.65+logit(.01)/log(10),label = "p = 0.01", hjust=0)+
     geom_hline(yintercept = logit(.99999)/log(10), linetype = 2, color = "grey") +
     annotate("text", x=.6,y=0.65+logit(.99999)/log(10),label = "p = 0.99999", hjust=0)+
     geom_hline(yintercept = logit(.00001)/log(10), linetype = 2, color = "grey") +
     annotate("text", x=.6,y=0.65+logit(.00001)/log(10),label = "p = 0.00001", hjust=0)+
    scale_x_discrete(limits = c("","","2","3","4","5","6","7","8","9"))+
            ylab(expression(paste(Log[10]," odds of match"))) + 
            xlab(element_blank()) +
             scale_fill_discrete(name = element_blank(), drop = FALSE, labels = c("match", "non-match")) + 
            NULL
ggsave("Nature-by-image-number.pdf", width = 5, height = 4)

ggplot(data = (filter(finalodds, !(model %in% c("2","3")), sets == "13579", df == 10)),mapping = aes(x = factor(k), y = logodds, fill = matching)) +
    geom_boxplot(position = position_dodge(width = .3)) +
    theme_bw(base_size = 13) +
  xlab("Number of images")+
    theme(legend.position = c(0.01,.99), legend.justification = c(0,1), legend.background = element_rect(), panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    geom_hline(yintercept = 0) + 
    annotate("text", x=.6,y=0.65,label = "p = 0.5", hjust=0)+
    geom_hline(yintercept = logit(.99)/log(10), linetype = 2, color = "grey") +
        annotate("text", x=.6,y=(.65+logit(.99)/log(10)),label = "p = 0.99", hjust=0)+
    geom_hline(yintercept = logit(.01)/log(10), linetype = 2, color = "grey") +
     annotate("text", x=.6,y=0.65+logit(.01)/log(10),label = "p = 0.01", hjust=0)+
     geom_hline(yintercept = logit(.99999)/log(10), linetype = 2, color = "grey") +
#    geom_text(aes(0,logit(.99999)/log(10),label = "p = 0.99999", vjust = -.5, hjust = -.1)) +
     annotate("text", x=.6,y=0.65+logit(.99999)/log(10),label = "p = 0.99999", hjust=0)+
     geom_hline(yintercept = logit(.00001)/log(10), linetype = 2, color = "grey") +
     annotate("text", x=.6,y=0.65+logit(.00001)/log(10),label = "p = 0.00001", hjust=0)+
    scale_x_discrete(limits = c("","","2","3","4","5"))+
            ylab(expression(paste(Log[10]," odds of match"))) + 
            xlab(element_blank()) +
             scale_fill_discrete(name = element_blank(), drop = FALSE, labels = c("match", "non-match")) + 
            NULL



ggplot(data = (filter(finalodds, !(model %in% c("2","3")), sets == "159", df == 10)),mapping = aes(x = factor(k), y = logodds, fill = matching)) +
    geom_boxplot(position = position_dodge(width = .3)) +
    theme_bw(base_size = 13) +
  xlab("Number of images")+
    theme(legend.position = c(0.01,.99), legend.justification = c(0,1), legend.background = element_rect(), panel.background = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
    geom_hline(yintercept = 0) + 
    annotate("text", x=.6,y=0.65,label = "p = 0.5", hjust=0)+
    geom_hline(yintercept = logit(.99)/log(10), linetype = 2, color = "grey") +
        annotate("text", x=.6,y=(.65+logit(.99)/log(10)),label = "p = 0.99", hjust=0)+
    geom_hline(yintercept = logit(.01)/log(10), linetype = 2, color = "grey") +
     annotate("text", x=.6,y=0.65+logit(.01)/log(10),label = "p = 0.01", hjust=0)+
     geom_hline(yintercept = logit(.99999)/log(10), linetype = 2, color = "grey") +
     annotate("text", x=.6,y=0.65+logit(.99999)/log(10),label = "p = 0.99999", hjust=0)+
     geom_hline(yintercept = logit(.00001)/log(10), linetype = 2, color = "grey") +
     annotate("text", x=.6,y=0.65+logit(.00001)/log(10),label = "p = 0.00001", hjust=0)+
    scale_x_discrete(limits = c("","","2","3"))+
            ylab(expression(paste(Log[10]," odds of match"))) + 
            xlab(element_blank()) +
             scale_fill_discrete(name = element_blank(), drop = FALSE, labels = c("match", "non-match")) + 
            NULL

```



```{r bysurface, fig.width =6, fig.height = 6}


dftextlabel = data.frame(untransformed = c(.99, .99999, .01, .00001), images = "9 images", 
                         stuff = c("p = 0.99", "p = 0.99999", "p = 0.01", "p = 0.00001"),
                         DF = ordered(rep("30",4), levels = c("3","5","10","15","20","30"))
                           , match = c("nonmatch", "nonmatch", "match", "match"),
                         model = factor(c("1",      "K-9-9-01",
                                        "S-10-09-02-01",  "S-10-9-10-01"),
                                        levels = c("1",      "K-9-9-01",
                                        "S-10-09-02-01",  "S-10-9-10-01"),
                                        labels = c("K-1-1", "K-2", "S-1", "S-2")))

df_fix_height = data.frame(logodds = c(16,16,16,28,28,28), images = "9 images",
                           DF = c("3","5","10","15","20","30"), model =  "K-9-9-01")

dftextlabel = dftextlabel %>% mutate(logodds = logit(untransformed)/log(10)+.65)

dflabs = c("DF = 3", "DF = 5", "DF = 10", "DF = 15", "DF = 20", "DF = 30")
finalodds$logodds = finalodds$classes/log(10)

names(dflabs) = c("3", "5", "10", "15", "20", "30")
finalodds$DF = finalodds$factordf
ggplot(data = filter(finalodds, k == 9), aes(x = match, y = logodds, 
                                                         fill = factor(model, labels = c("K-1-1", "K-2", "S-1", "S-2")))) +
  labs(title = "", x = "", 
       y = expression(paste(Log[10]," odds of match"))) +
  geom_boxplot() + 
  geom_hline(yintercept = 0) +
 facet_wrap(~DF, labeller = label_both ) +
  theme_bw() +
 scale_fill_discrete(name="Training Set")+
  scale_x_discrete(labels = c("match", "non-match"))+
  theme(legend.position = "bottom", legend.spacing.y = unit(2,"cm")) +

       geom_hline(yintercept = logit(.99)/log(10), linetype = 2, color = "grey") +
    geom_hline(yintercept = logit(.01)/log(10), linetype = 2, color = "grey") +
     geom_hline(yintercept = logit(.99999)/log(10), linetype = 2, color = "grey") +
     geom_hline(yintercept = logit(.00001)/log(10), linetype = 2, color = "grey") +
       geom_text(data = dftextlabel, mapping = aes(x = match, y = logodds, label = stuff), size = 2.5)+
  NULL
ggsave("Nature-bysurface.pdf", height = 5, width = 6)

```

## Log Odds of extreme value boundary


```{r pivot, echo = TRUE}
bounddata <- finalodds %>% filter(k ==9, factordf == "10", 
                                  model == "S-10-09-02-01", match == "nonmatch" )

 xbar = mean(bounddata$classes)
 se = sd(bounddata$classes)
 n = 324
 delta = -(sqrt(n-1)) * qnorm(.9999)
res = xbar - qt(0.05, n-1,delta) * se / sqrt(n)
res

cat("probability:")

1/(1+exp(-res))
```


## Cross Validation Information


```{r combinedcvdata, fig.width=5.5, fig.height=4}
ninecvdf = read.csv('data/nine-image-CV-results.csv')
ninecvdf$images = "9 images"

threecvdf = read.csv('data/three-image-CV-results.csv')
threecvdf$images = "3 images"

fivecvdf = read.csv('data/five-image-CV-results.csv')
fivecvdf$images = "5 images"

combcvdf = rbind(ninecvdf, fivecvdf, threecvdf)

library(ggplot2)
invlogit = function(x) 1/(1+exp(-x))

textlabeldf = data.frame(untransformed = c(.99, .99999, .01, .00001), images = "9 images", 
                         label = c("p = 0.99", "p = 0.99999", "p = 0.01", "p = 0.00001"),
                         df = 3, matching = "match")

textlabeldf = textlabeldf %>% mutate(logodds = logit(untransformed)/log(10))


qplot(matching, logodds, fill = factor(df), data = combcvdf, geom = "boxplot", facets = ~images)+
  theme_bw()+
  xlab(NULL)+
  ylab(expression(paste(Log[10]," odds of match"))) +
  labs(fill = "DF")+
  geom_hline(yintercept=0)+
   theme(legend.position = "bottom") +
    guides(fill = guide_legend(nrow=1, ncol = 6))+
  scale_fill_brewer(palette = "Dark2")+
  scale_x_discrete(labels = c("match", "non-match"))+
     geom_hline(yintercept = logit(.99)/log(10), linetype = 2, color = "grey") +
    geom_hline(yintercept = logit(.01)/log(10), linetype = 2, color = "grey") +
     geom_hline(yintercept = logit(.99999)/log(10), linetype = 2, color = "grey") +
     geom_hline(yintercept = logit(.00001)/log(10), linetype = 2, color = "grey") +
   geom_text(data = textlabeldf, mapping = aes(x = matching, y = logodds, label = label), size = 3)+
  NULL

ggsave("combined-image-CV.pdf", width = 5.5, height = 4)

```





```{r Nature-repeatability, fig.height = 4, fig.width = 4}

newcorset = rbind(cor.set1,cor.set2,cor.set3)
newcorset$zfive = fisherz(newcorset$`5-10`)
newcorset$zten = fisherz(newcorset$`10-20`)

newcorset$repetition = factor(newcorset$set)
newcorset$img = factor(newcorset$img)
matchset = newcorset[newcorset$match == "match",]
matchset = droplevels(matchset)
fisher_trans = function() trans_new("fisher", function(x) psych::fisherz(x), 
                                    function(x) psych::fisherz2r(x))

#str(newcorset)

library(ellipse)

pickpoints <- newcorset$match == 'match'




newcorset$x = newcorset$`5-10`
newcorset$y = newcorset$`10-20`

newcorset$set = factor(newcorset$set, levels = c("1", "2", "3"),
                       labels = c("K-1-1", "K-1-2", "K-1-3"))

newmeans <- newcorset %>% filter(match == 'match') %>% group_by(set) %>% summarize(x = mean(x), y = mean(y)) 
library(ellipse)
peacocksubset =  newcorset[pickpoints,c("x","y","repetition")] # this is a bad way of doing it

rot.one = subset(peacocksubset, repetition == "1")[,c("x","y")]
rot.two = subset(peacocksubset, repetition == "2")[,c("x","y")]
rot.three = subset(peacocksubset, repetition == "3")[,c("x","y")]

centers = c(mean(atanh(rot.one$x)),mean(atanh(rot.one$y)))
cov = cov(atanh(rot.one[,c('x','y')]))
ellipsepoints = data.frame(tanh(ellipse(centre =centers, cov,level = .99, npoints = 300)))
ellipsepoints$set = "K-1-1"

centers = c(mean(atanh(rot.two$x)),mean(atanh(rot.two$y)))
cov = cov(atanh(rot.three[,c('x','y')]))
ellipsepointstwo = data.frame(tanh(ellipse(centre =centers, cov,level = .99, npoints = 300)))
ellipsepointstwo$set = "K-1-2"

ellipsepoints = rbind(ellipsepoints, ellipsepointstwo)


centers = c(mean(atanh(rot.three$x)),mean(atanh(rot.three$y)))
cov = cov(atanh(rot.three[,c('x','y')]))
ellipsepointstwo = data.frame(tanh(ellipse(centre =centers, cov,level = .99, npoints = 300)))
ellipsepointstwo$set = "K-1-3"

ellipsepoints = rbind(ellipsepoints, ellipsepointstwo)

ellipsepoints$set = factor(ellipsepoints$set, levels = c("K-1-1", "K-1-2", "K-1-3"),
                       labels = c("K-1-1", "K-1-2", "K-1-3"))


threesets = ggplot(mapping = aes(x=x, y=y, color = set)) +
    geom_point(data = newcorset[pickpoints,], mapping = aes(shape = set), alpha = I(1))+
    geom_point(data = newmeans,  mapping = aes(shape = set), size = 5) +
    geom_path(data = ellipsepoints, lty = 2, size = 1) +

    theme_bw() +
    theme(          legend.justification=c(0,1), legend.position=c(0.001,.999),
          legend.text =element_text(size = 10), legend.title = element_blank(),
          legend.background = element_rect(fill = "white", color = "black"), legend.box.background = element_rect(colour = "black")) +
    coord_trans(x = "fisher", y = "fisher") +
    labs(color = "Set", shape = "Set", x="5-10 frequency range",
         y="10-20 frequency range" ) +
    scale_y_continuous(breaks = c(-.15,0,.25,.5,.75,.90,.95,.99)) +
    scale_x_continuous(breaks = c(-.25,0,.25,.5,.75,.90,.95,.99)) +
    scale_color_manual(values = c("#1b9e77", "#d95f02", "#7570b3"))+
    scale_fill_manual(values = c("#1b9e77", "#d95f02", "#7570b3"))+
    NULL
    threesets
    
library(Peacock.test) # https://www.sciencedirect.com/science/article/pii/S0167947316301785

### NOTE: atanh of this will give the same values b/c it's a monotonic transformation
### and this is a rank-based test
print("Peacock test results:\n\n")
    
    
peacock2((rot.one),(rot.two)) # [1] 0.2098765

peacock2(rot.two,rot.three) # [1] 0.2469136

peacock2(rot.one,rot.three) # [1] 0.3209877

    
    
```






```{r Nature-scatterplot, fig.height = 5, fig.width = 5}

library(cowplot)
totalcorset = totalcorset %>% mutate(nmatch = case_when(match == "match" ~ "match", match == "nonmatch" ~ "non-match"))
smallcorset <- totalcorset %>% filter(set == "1")

smallcorset$x = smallcorset$`5-10`
smallcorset$y = smallcorset$`10-20`

lineset <- smallcorset %>% filter(knife == "T10:T10") %>% arrange(x)
totalcorset$x = totalcorset$`5-10`
totalcorset$y = totalcorset$`10-20`


########## variances (in transformed space)

totalcorset$zx = atanh(totalcorset$x )
totalcorset$zy = atanh(totalcorset$y )

matchz = totalcorset %>% filter(nmatch == "match") %>% select(zx, zy) %>% colMeans()
nonmatchz = totalcorset %>% filter(nmatch == "non-match") %>% select(zx, zy) %>% colMeans()

matchzdf = data.frame(zx = rep(matchz[1], 100), zy = rep(matchz[2], 100))
nonmatchzdf = data.frame(zx = rep(nonmatchz[1], 100), zy = rep(nonmatchz[2], 100))


matchmean = tanh(matchz)
names(matchmean) = c("x", "y")

nonmatchmean = tanh(nonmatchz)
names(nonmatchmean) = c("x", "y")

matchvar = totalcorset %>% filter(match == "match") %>% select(zx, zy) %>% var

nonmatchvar = totalcorset %>% filter(match == "nonmatch") %>% select(zx, zy) %>% var

########### t distribution stuff
library(mvtnorm) 

nu <- 10
rtsq <- rowSums(x = matrix(rt(n = 2e6, df = nu)^2, ncol = 2)) 


############

lineset <- totalcorset %>% filter(knife == "T10:T10") %>% arrange(x)


newellipseplot = ggplot(mapping = aes(x=x, y=y)) +
  geom_point(data = totalcorset, mapping = aes(shape = nmatch, color = nmatch, alpha = I(0.01)))+
  guides(alpha=FALSE, fill = FALSE)+
    theme_bw() +
  theme(          legend.justification=c(0,1), legend.position=c(0,1),
                  legend.text =element_text(size = 11), legend.title = element_blank(),
                  legend.background = element_rect(fill = "white", color = "black"), axis.text.x = element_text( angle = 45, hjust = 1 ),
                  legend.box.background = element_rect(colour = "black"),
                  legend.spacing.y = unit(0, "mm")) +
  labs(color = element_blank(), shape = element_blank(), x="5-10 frequency range",
       y="10-20 frequency range" ) +
  scale_y_continuous(trans = "fisher",breaks = c(-.15,0,.25,.5,.75,.90,.95,.99), limits = c(-.197,.96)) +
  scale_x_continuous(trans = "fisher", breaks = c(-.25,0,.25,.5,.75,.90,.95,.99), limits = c(-.5,.995)) +
  scale_color_manual(values = c("match" = "#7F2704", "non-match" = "#00441B"))+
    scale_fill_manual(values = c("match" = "#7F2704", "non-match" = "#00441B"))+
  NULL

######### add ellipses


for (i in seq(from = 0.10, to = 0.95, length.out = 50)) {    
 
el.df <- data.frame(tanh((matchzdf) + ellipse(x = matchvar, t = sqrt(quantile(rtsq, probs = (i)))))) ## create the data for the given quantile of the ellipse.    
el1.df <- data.frame(tanh((nonmatchzdf)+ellipse(x = nonmatchvar, t = sqrt(quantile(rtsq, probs = (i))))))
names(el.df) <- c("x", "y")
names(el1.df) <- c("x", "y")


newellipseplot <- newellipseplot + 
  geom_polygon(data=el.df, aes(x=x, y=y), fill = "#D94801", colour = NA, alpha = I(0.02)) + 
  geom_polygon(data=el1.df, aes(x=x, y=y), fill = "#238B45", colour = NA, alpha = I(0.01))
}

###### add line, points back on top
newellipseplot <- newellipseplot + 
  geom_path(data = lineset, color = "blue") +
  geom_point(data = totalcorset, mapping = aes(shape = nmatch, color = nmatch, alpha = I(0.6)))+
  NULL
  
#########

#newellipseplot
xdens <- axis_canvas(newellipseplot, axis = 'x') + 
  geom_histogram(data = totalcorset, mapping = aes(x = (x), after_stat(density), fill = nmatch, alpha = I(0.4)), position = 'identity') +
  geom_density(data = totalcorset, mapping = aes(x = (x), color = nmatch))+
  scale_fill_manual(values = c("match" = "#D94801", "non-match" = "#238B45"))+
  scale_color_manual(values = c("match" = "#7F2704", "non-match" = "#00441B"))+
  scale_x_continuous(trans = "fisher", limits = c(-.5,.995)) +
  NULL
ydens <- axis_canvas(newellipseplot, axis = 'y', coord_flip = TRUE) + 
  geom_histogram(data = totalcorset, mapping = aes(x = (y), after_stat(density), fill = nmatch,  alpha = I(0.4)), position = 'identity') +
  geom_density(data = totalcorset, mapping = aes(x = (y), color = nmatch))+
  scale_fill_manual(values = c("match" = "#D94801", "non-match" = "#238B45"))+
  scale_color_manual(values = c("match" = "#7F2704", "non-match" = "#00441B"))+
  scale_x_continuous(trans = "fisher",breaks = c(-.15,0,.25,.5,.75,.90,.95,.99), limits = c(-.197,.96)) +
  coord_flip() +
  NULL
onep1 <- insert_xaxis_grob(newellipseplot, xdens, grid::unit(.2, 'null'), position = "top")
onep2 <- insert_yaxis_grob(onep1, ydens, grid::unit(.2, 'null'), position = 'right')
ggdraw(onep2)


```

## Probability table

This table is not in the supplement.

```{r probs, asis=TRUE}
invlogit = function(x) 1/(1+exp(-x))

knitr::kable(finalodds %>% group_by(matching, sets, factordf) %>% 
               filter(k == "2") %>%
               summarize(max = round(max(invlogit(classes)),4), 
                         min = round(min(invlogit(classes)), 4), 
                         q_01 =  round(invlogit(quantile((classes), 0.01)), 4), 
                         q_05 = round(invlogit(quantile((classes), 0.05)), 4), 
                         q_95 = round(invlogit(quantile((classes), 0.95)), 4), 
                         q_99 = round(invlogit(quantile((classes), 0.99)), 4) ),
             caption = "Quantiles of classification probabilities (Min, Max, 0.01, 0.05, 0.95, and 0.99) for models trained on the 75%, 50%, and 0% overlap sets and tested with k = 2 images.")
```


```{r calibplot}
dev_data=finalodds %>% mutate(pred = invlogit(classes)) %>%  
  mutate(adj_pred = invlogit(classes+logit(.09413))) %>%  
  filter(pred >.001, pred < .999) %>% 
  mutate(y = case_when(
    matching == "match" ~ 1,
    TRUE ~ 0 ))

ggplot(dev_data, aes(pred, y, color = factordf)) +
  geom_abline(slope = 1, intercept = 0) +
  geom_smooth(method = "loess", se = FALSE, span = .06) +
  scale_x_continuous(breaks = seq(0, 1, 0.1)) +
  scale_y_continuous(breaks = seq(0, 1, 0.1)) +
  scale_color_brewer(palette="Dark2")+
  xlab("Estimated Probability") +
    theme_bw()+
  ylab("Data w/ Empirical Proportion") +
  labs(color = "DF")+
    # ggtitle("Logistic Regression Calibration Plot") + 
  NULL
  
ggsave("calibplot.pdf", height = 4, width = 5.5)  

```


